Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-01-09 paper.tex
Mehr sinnlose Bilder

\subsection{Applications to material images}
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table*}
In this section we compute correlation functions for 2- and 3-dimensional real
samples. Table \ref{tab:summary} contains information about these samples. Note
that we compute surface correlation functions only for those samples for which
the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
of the samples are on \cref{fig:samples}. On plots of correlation functions for
isotropic samples we provide a family of curves with the first argument of the
correlation function being fixed. For anisotropic samples we provide heatmaps of
correlation functions where anisotropy can be easily observed.
\begin{figure*}[tp]
  \centering
  \subfigure[Sanstone XCT]{
    \includegraphics[width=0.4\linewidth]{images/15581.png}
    \label{fig:sample-sandstone-xct}}
  \hfill
  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

@@

The anisotropic samples (the soil and the shale) were preliminarily rotated with
periodic boundary conditions to align elongated pores with coordinate axes. The
result of rotation can be seen on \cref{fig:samples-rot}. Heatmaps of $S_3$
function for these samples can be seen on \cref{fig:heatmaps}. It can be
observed that elongated clusters of the void phase in the sample of soil form a
structure which resembles a regular grid with spacing of about $60 \mu m$. The
sample of shale shows less regular yet still anisotropic structure.

@@

>>>>

\subsection{Applications to material images}
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m / px$)
    & $C_{0.5}$ & Comment \\
    \hline
    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 & \\
    Soil & XCT & $500 \times 500 \times 500$ & 0.72 & 0.9431 & Digitally
    magnified \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 & \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 & \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table*}
In this section we compute correlation functions for 2- and 3-dimensional real
samples. Table \ref{tab:summary} contains information about these samples. Note
that we compute surface correlation functions only for those samples for which
the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil). Images
of the samples are on \cref{fig:samples}. On plots of correlation functions for
isotropic samples we provide a family of curves with the first argument of the
correlation function being fixed. For anisotropic samples we provide heatmaps of
correlation functions where anisotropy can be easily observed.
\begin{figure*}[tp]
  \centering
  \subfigure[Sanstone XCT]{
    \includegraphics[width=0.4\linewidth]{images/15581.png}
    \label{fig:sample-sandstone-xct}}
  \hfill
  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

@@

The anisotropic samples (the soil and the shale) were preliminarily rotated with
periodic boundary conditions to align elongated pores with coordinate axes. The
result of rotation can be seen on \cref{fig:samples-rot}. Heatmaps of $S_3$
function for these samples can be seen on \cref{fig:heatmaps}. It can be
observed that elongated clusters of the void phase in the sample of soil form a
structure which resembles a regular grid with spacing of about $60 \mu m$. The
sample of shale shows less regular yet still anisotropic structure. We provide
the rest of correlation functions for the sample of soil on
\cref{fig:soil-maps}.

@@

\begin{figure*}[tp]
  \centering
  \subfigure[$C_3$]{
    \includegraphics[width=0.4\linewidth]{images/c3-map.png}}
  \hfill
  \subfigure[$F_{sss}$]{
    \includegraphics[width=0.4\linewidth]{images/surf3-map.png}}
  \vskip\baselineskip
  \subfigure[$F_{ssv}$]{
    \includegraphics[width=0.4\linewidth]{images/surf2void-map.png}}
  \hfill
  \subfigure[$F_{svv}$]{
    \includegraphics[width=0.4\linewidth]{images/surfvoid2-map.png}}
  \caption[]{Correlation maps for the sample of soil.}
  \label{fig:soil-maps}
\end{figure*}
